%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.3, 10 May 2020) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% (v1.6.5b, 27 Jun 2023) forked by Nicolás Omar González Passerino (nicolas.passerino@gmail.com)
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

%% Fork (before v1.6.5a): CV dark mode toggle enabler to use a inverted color palette.
%% Use the "darkmode" option if you want a color palette used to 
% \documentclass[10pt,a4paper,ragged2e,withhyper,darkmode]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 and academicons fonts
%% and packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1cm,right=1cm,top=0.75cm,bottom=0.75cm,columnsep=0.75cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Fork (before v1.6.5a): Change the color codes to test your personal variant on any mode
\ifdarkmode%
  \definecolor{PrimaryColor}{HTML}{C69749}
  \definecolor{SecondaryColor}{HTML}{D49B54}
  \definecolor{ThirdColor}{HTML}{1877E8}
  \definecolor{BodyColor}{HTML}{ABABAB}
  \definecolor{EmphasisColor}{HTML}{ABABAB}
  \definecolor{BackgroundColor}{HTML}{FFFFFF}
\else%
  \definecolor{PrimaryColor}{HTML}{15317D} % Dark blue
  \definecolor{SecondaryColor}{HTML}{46588A} % Grey blue
  \definecolor{ThirdColor}{HTML}{C2980E} % Gold
  \definecolor{BodyColor}{HTML}{666666} % Lighter grey
  \definecolor{EmphasisColor}{HTML}{2E2E2E} % Dark grey
  \definecolor{BackgroundColor}{HTML}{FFFFFF} % White
\fi%

\colorlet{name}{PrimaryColor}
\colorlet{tagline}{SecondaryColor}
\colorlet{heading}{PrimaryColor}
\colorlet{headingrule}{ThirdColor}
\colorlet{subheading}{SecondaryColor}
\colorlet{accent}{SecondaryColor}
\colorlet{emphasis}{EmphasisColor}
\colorlet{body}{BodyColor}
\pagecolor{BackgroundColor}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\small\bfseries}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}
\renewcommand{\profilefont}{\small}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\usepackage{amssymb}


\begin{document}
\name{Patrick Moehrke}
\tagline{TASSA | Actuarial Consultant}

\personalinfo{

  \email{patrickmoehrke46@gmail.com}\\\smallskip
  \linkedin{patrick-moehrke-05b09ab3}\\\smallskip
  \github{patrickm663}\\\smallskip
  \location{Somerset West, Western Cape, ZA}\\\smallskip
  \worklocation{Open to on-premise, hybrid, and remote work}
}
\profile{
  I am an aspiring actuary with a strong focus on developing \& contributing to open-source tools for reporting and analytics. I am also a keen software developer with a high aptitude for probabilistic programming, machine learning \& cloud.
}

\makecvheader
% ----- PROFILE -----

% ----- PROFILE -----
%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\normalsize}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.29}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

  % ----- SKILLS -----
  \cvsection{Skills}
  \cvsubsection{Interpersonal Skills}
  \cvtag{Life-long learner}
  \cvtag{Self-starter}
  \cvtag{Problem solver}
  \cvtag{Innovator}
  \cvtag{Critical thinker}
  \cvtag{Collaborator}
  \cvtag{Public speaker}
  \medskip

  \cvsubsection{Technical Skills}
  \cvtag{Bayesian statistics}
  \cvtag{IFRS 17}
  \cvtag{Automation}
  \cvtag{Dashboarding}
  \cvtag{Cloud computing}
  \cvtag{Research}
  \cvtag{Machine learning}
  \cvtag{XAI}\\
  \cvtag{Solution architecture}\\
  \cvtag{Experience analysis}\\
  \cvtag{Actuarial modelling}\\
  \medskip

  \cvsubsection{Tech Stack}
  \cvtag{Julia}
  \cvtag{Python}
  \cvtag{R}
  \cvtag{SQL}\\
  \cvtag{Bash}
  \cvtag{Turing.jl}
  \cvtag{Shapley}\\
  \cvtag{Docker}
  \cvtag{Linux}
  \cvtag{\LaTeX}\\
  \cvtag{GitHub Actions}
  \cvtag{AWS}
  \cvtag{Git}
  \cvtag{Neovim}
  \cvtag{Microsoft Excel}
  \cvtag{Terraform}
  \cvtag{Streamlit}
  \cvtag{Shiny}

  % ----- SKILLS -----



  % ----- ACTUARIAL EDUCATION -----

  \cvsection{Actuarial \\Education}
  \cvsubsection{Exam Passes}
  \cvtag{A111-A214}
  \cvtag{N111}
  \cvtag{N211}
  \cvtag{F104}\\
  \medskip

  \cvsubsection{\emph{In Progress}}
  \cvtag{A311}
  \cvtag{F105}
  \cvtag{N311}
  \medskip

  % ----- ACTUARIAL EDUCATION -----



  % ----- AWARDS & CERTIFICATIONS -----

  \cvsection{Certifications} 
  \begin{itemize}[label=$\circ$, leftmargin=0.33cm, labelsep=0.2cm]\bfseries
    \item AWS Solutions Architect \\Associate\\
    \item AWS Certified Cloud \\Practitioner\\
  \end{itemize}
  \smallskip

  \newpage

  \cvsection{Awards} 
  \begin{itemize}[label=$\circ$, leftmargin=0.33cm, labelsep=0.2cm]\bfseries
    \item Member of Golden Key \\International Honours Society\\
    \item Stellenbosch University Dean's\\ Merit List for 6 Subjects\\
    \item Stellenbosch University Merit Bursary
    \item Maties Gymnastics's \textit{Matie of the Year} 
  \end{itemize}

  % ----- AWARDS & CERTIFICATIONS -----


  % ----- INTERESTS -----

  \cvsection{Interests \&\\Hobbies}

  \cvsubsection{Interests}
  \cvtag{Cloud native technologies}\\
  \cvtag{Scientific machine learning}
  \cvtag{Probabilisitc programming}\\
  \cvtag{Video game development}\\
  \cvtag{Linux development}
  \medskip

  \cvsubsection{Hobbies}
  \cvtag{Reading}
  \cvtag{Travelling}\\
  \cvtag{Gymnastics}
  \cvtag{Video games}\\
  \cvtag{Recreational programming}
  \medskip

  % ----- INTERESTS -----



  % ----- REFERENCES -----

  \medskip	
  \cvsection{References}
  \cvevent{Available upon request.}{}{}{}

  % ----- REFERENCES -----

  %% Switch to the right column. This will now automatically move to the second
  %% page if the content is too long.
  \switchcolumn


  % ----- EXPERIENCE -----

  \cvsection{Experience}
  \smallskip
  \cvevent{Actuarial Consultant}{Actuartech}{January 2022 -- Present}{}
  \smallskip
  \cvsubsection{Analytics}
  \begin{itemize}[label=$\circ$, leftmargin=0.9cm, labelsep=0.43cm]
    \item Assisted in delivering \& presenting end-to-end mortality experience analyses to management of a South African life insurer.
    \item Conducted research into various ways open-source packages can improve \\actuarial analytics, including deep learning and Bayesian analysis using Julia.
    \item Developed and presented training material on actuarial \\data science to actuarial functions (mainly South African \& UK life insurers). Software included R, Python, SQL, GitHub \& serverless AWS services. 
    \item As part of a global research team, conducted research on AI risk for actuarial teams. This included fairness modelling, evidencing proxy discrimination \& demonstrating model explainability techniques using driver telematics data. 
    \item Co-presented on actuarial data science risk management at the ASSA 2022 and IFoA 2022 conferences. 
  \end{itemize}

  \cvsubsection{Reporting}
  \begin{itemize}[label=$\circ$, leftmargin=0.9cm, labelsep=0.43cm]
    \item Assisted in delivering a fully restrospective Opening Balance under IFRS 17's GMM and VFA measurement models for a South African life insurer. 
    \item Engaged with auditors to provide a first draft of IFRS 17 VFA methodology for a South African subsidary of a UK life insurer. 
    \item Developed, architected, and deployed a serverless data management \&\\ dashboarding solution on AWS to report financial results aligned to IFRS 17 at a reduced cost vs off-the-shelf solutions.
    \item Developed, tested, and documented a financial reporting solution for a South African life insurer to ensure compliance with IFRS 17.
    \item Assisted in developing \& presenting workshops on IFRS 17 to members of the Lloyds of London. 
    \item Co-presented on IFRS 17 reporting using Python at the ASSA 2023 \\conference. 
  \end{itemize}

  \cvsubsection{Infrastructure}
  \begin{itemize}[label=$\circ$, leftmargin=0.9cm, labelsep=0.43cm]
    \item Identified and documented risks present in the current architecture of a multinational reinsurer's actuarial \& financial reporting solution, and proposed a\\ future implementation state to stakeholders.
    \item Architected, tested, and developed a low-cost, full-stack serverless web \\application to conference attendees over 3 days, handling +3 000 API calls with zero failures.
    \item Gained exposure to monitoring the cloud costs of actuarial systems \& \\investigated solutions to reduce the cost of Kubernetes instances on AWS. 
  \end{itemize}

  \medskip 
  \cvevent{Junior Actuarial Consultant}{Actuartech}{July 2020 -- December 2021}{}
  \smallskip
  \cvsubsection{Analytics}
  \begin{itemize}[label=$\circ$, leftmargin=0.9cm, labelsep=0.43cm]
    \item Assisted in creating \& presenting bespoke R training courses for clients in South African life insurers.
    \item Under supervision, conducted surveys with actuarial managers to benchmark the use of data science \& analytics across South African \& UK actuarial teams. 
    \item Co-facilitated webinars \& talks to regional actuarial societies on the topic of actuarial data science. 
  \end{itemize}

  \cvsubsection{Reporting}
  \begin{itemize}[label=$\circ$, leftmargin=0.9cm, labelsep=0.43cm]
    \item Assisted in developing \& presenting workshops on IFRS 17 to regional \\actuarial societies. 
    \item Assisted in conducting an IFRS 17 readiness \& gap analysis for a South African life insurer. 
    \item Worked with the client to dashboard indicative IFRS 17 results under GMM \& PAA measurement models. 
  \end{itemize}

  \cvsubsection{Infrastructure}
  \begin{itemize}[label=$\circ$, leftmargin=0.9cm, labelsep=0.43cm]
    \item Assisted in drafting \& presenting training material aimed at actuaries wanting to understand DevOps tooling. This included material on containers, CICD, cloud, infrastructure-as-code \& monitoring tools. 
    \item Gained exposure to architectural \& maintainance aspects of a Kubernetes-hosted JupyterHub platform. 
  \end{itemize}

  \medskip 

  \cvevent{Academic Tutor}{Stellenbosch University}{January 2020 -- July 2020}{}
  \smallskip
  I served as an academic tutor for Actuarial Science 112 (financial mathematics).\\ This included mentoring, explaining mathematical topics in simple terms \& reviewing assignments. 

  \bigskip 
  % ----- EXPERIENCE -----
  
  %\newpage

  % ----- EDUCATION -----
  \cvsection{Education}
  \smallskip
  \cvevent{BCom Honours Actuarial Science}{Stellenbosch University}{Jan 2020 -- Dec 2020}{}
  \smallskip
  \cvsubsubsection{Research Project}
  Evaluating the use of genetics to calculate risk premiums with applications to \\Huntington's Disease.\\

  Supervisor: Mr Werner Weber, FASSA\\
  \smallskip
  \cvsubsubsection{Subjects}
  Actuarial risk management, financial engineering, extreme value theory, statistical programming in R \& communications.\\
  \smallskip
  \cvsubsubsection{Activities}
  Maties Gymnastics Chairperson \& USSA Gymnastics Vice-chairperson. 

  \medskip
  \cvevent{BCom Actuarial Science}{Stellenbosch University}{Jan 2017 -- Dec 2019}{}
  \smallskip
  \cvsubsubsection{Subjects}
  Actuarial science, mathematical statistics, computer science, mathematics \& \\economics.\\
  \smallskip
  \cvsubsubsection{Activities}
  Maties Gymnastics Treasurer, USSA Gymnastics Vice-chairperson \& Helderberg Men's Residence Entrance Captain.

  \medskip
  \cvevent{IEB National Senior Certificate}{Beaulieu College}{Jan 2012 -- Dec 2016}{}
  \smallskip
  \cvsubsubsection{Subjects}
  IEB matric certificate with an A average. Awarded top achiever in Accounting, \\Mathematics \& AP Mathematics.\\
  \smallskip
  \cvsubsubsection{Activities}
  Prefect (Head of House). Rugby, water polo \& chess.

  % ----- EDUCATION -----


\end{paracol}
\end{document}
